\section{Related Files}

The related files to this thesis are attached on a USB stick.

\begin{description}
    \item[SEE\_Desktop.zip] \label{file:desktop} The desktop version of \gls{see} used for the user study. Unzip and start by executing the \textit{See.exe}
    \item[SEE\_Mobile.apk] The \gls{android} version of \gls{see} that is used for the user study. The file can be installed on an \gls{android} device.
    \item[SEE\_final.apk] A revised \gls{android} version of \gls{see}. Zooming is inverted, and the application is flipped 180° as it was heavily requested in the user study.
    \item[calc\_data.ipynb] \label{calc} A Python script that calculates all results of the study.
    \item[See Desktop - See Mobile.csv] The survey answers from \textit{Group 1}. The subjects started with the desktop version of \gls{see}.
    \item[See Mobile - See Desktop.csv] The survey answers from \textit{Group 2}. The subjects started with the mobile version of \gls{see}.
    \item[See\_Mobile.mp4] The instruction video for the mobile version of \gls{see} used in the user study.
    \item[See\_Desktop.mp4] The instruction video for the desktop version of \gls{see} used in the user study.
    \item[User\_Manual\_See.pdf] A short overview for the interactions in the mobile version of \gls{see}.
    \item[See\_mobile\_repository.zip] The repository for \gls{see} containing all the changes made for the mobile version. Note that \gls{see} is an ongoing project and only the changes discussed in chapter \ref{section:implementation} are part of this thesis.
\end{description}

